### 2019-05-24 doc/chapters/towards_verifying.tex
result image
issue -> pull request
rewriting objects

\subsection{Rewriting Objects}
// TODO reason? because we can not extend case object?
Stainless output:
\begin{lstlisting}
[ Error  ] CurrencyUnits.scala:54:1: Objects cannot extend classes or implement
           traits, use a case object instead
           object Satoshis extends BaseNumbers[Satoshis] {
\end{lstlisting}

@@

\subsection{Rewriting Type Member}
Stainless output:
\begin{lstlisting}
  [Warning ] NumberType.scala:5:3: Could not extract tree in class: type A
             = BigInt (class scala.reflect.internal.Trees$TypeDef)
             type A = BigInt
\end{lstlisting}
Since the type A is not overridden in any of its subclasses, this can simply be hard coded.
\begin{lstlisting}
  sealed abstract class Number {
    type A = BigInt
    protected def underlying: A
    def apply: A => T
  }
\end{lstlisting}
Replace every occurence of A with BigInt.
This might be a missing feature in Stainless that should not be to hard to fix.
There is an open issue on Github \mypound511.

@@

>>>>

\subsection{Rewriting Objects}
// TODO reason?

Stainless output:
\begin{lstlisting}
[ Error  ] CurrencyUnits.scala:54:1: Objects cannot extend classes or implement
           traits, use a case object instead
           object Satoshis extends BaseNumbers[Satoshis] {
\end{lstlisting}
Changing the objects that extends classes to case objects solves this problem.

@@

\subsection{Rewriting Type Member}
Stainless output:
\begin{lstlisting}
  [Warning ] NumberType.scala:5:3: Could not extract tree in class: type A
             = BigInt (class scala.reflect.internal.Trees$TypeDef)
             type A = BigInt
\end{lstlisting}
Since the type A is not overridden in any of its subclasses, this can simply be hard coded.
\begin{lstlisting}
  sealed abstract class Number {
    type A = BigInt
    protected def underlying: A
    def apply: A => T
  }
\end{lstlisting}
Replace every occurence of A with BigInt.
This might be a missing feature in Stainless that should not be to hard to fix.
There is an open pull request \mypound470 on Github for this issue.

@@

\section{Result}
\begin{figure}[H]
	\centering
		\includegraphics[scale=0.45]{images/final_verify_output.png}
	\caption{Output of Stainless verification for addition with 0 of Bitcoin-S-Cores CurrencyUnit}
	\label{fig:output1}
\end{figure}
